---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "tools/"
)
```

# bertini

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/bertini)](https://cran.r-project.org/package=bertini)
[![Travis build status](https://travis-ci.org/dkahle/bertini.svg?branch=master)](https://travis-ci.org/dkahle/bertini)
<!-- badges: end -->

__bertini__ is an R package that provides methods and data structures for [numerical algebraic geometry](https://en.wikipedia.org/wiki/Numerical_algebraic_geometry), the numerical solution to (nonlinear) systems of polynomial equations using homotopy continuation.


It is currently being developed.


_Note: the following assumes you have [Bertini](https://bertini.nd.edu) and bertini recognizes its path._

```{r load}
library("bertini")
```




## Basic usage

```{r basic-usage}
code <- "
INPUT

variable_group x, y;
function f, g;

f = x^2 + y^2 - 1;
g = y - x;

END;
"
bertini(code)
```








## Installation

* From Github (dev version): 
```{r, eval=FALSE}
if (!requireNamespace("devtools")) install.packages("devtools")
devtools::install_github("dkahle/mpoly")
devtools::install_github("dkahle/bertini")
```





## Acknowledgements

This material is based upon work supported by the National Science Foundation under Grant Nos. [1622449](https://nsf.gov/awardsearch/showAward?AWD_ID=1622449) and [1622369](https://www.nsf.gov/awardsearch/showAward?AWD_ID=1622369).
