---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "tools/"
)
```

# bertini

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/bertini)](https://cran.r-project.org/package=bertini)
[![Travis build status](https://travis-ci.org/dkahle/bertini.svg?branch=master)](https://travis-ci.org/dkahle/bertini)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/dkahle/bertini?branch=master&svg=true)](https://ci.appveyor.com/project/dkahle/bertini)
<!-- badges: end -->

__bertini__ is an R package that provides methods and data structures for [numerical algebraic geometry](https://en.wikipedia.org/wiki/Numerical_algebraic_geometry), the numerical solution to (nonlinear) systems of polynomial equations using homotopy continuation.


It is still experimental, but the core functionality in the zero-dimensional case is quite stable.


_Note: the following assumes you have [Bertini](https://bertini.nd.edu) and bertini recognizes its path._

```{r load}
library("bertini")
```




## Basic usage

```{r basic-usage}
code <- "
INPUT

variable_group x, y;
function f, g;

f = x^2 + y^2 - 1;
g = y - x;

END;
"
bertini(code)
```



## Solving zero-dimensional systems of polynomial equations

`poly_solve()` is the basic workhorse for solving systems of polynomial equations. For example, if we want to solve the system $y = x$ and $x^{2} + y^{2} = 1$, which corresponds geometrically to the points where the identity line intersects the unit circle, we can use:

```{r poly-solve}
poly_solve(c("y = x", "x^2 + y^2 = 1"), varorder = c("x", "y"))
```




## Polynomial optimization over compact varieties

`poly_optim()` can be used to find the critical points of polynomials over varieties.  For example, if we want to find the maximum value of the function $f(x,y) = x + y$ over the unit circle:

```{r poly-optim}
poly_optim("x + y", "x^2 + y^2 = 1")
```







## Installation

* From Github (dev version): 
```{r, eval=FALSE}
if (!requireNamespace("devtools")) install.packages("devtools")
devtools::install_github("dkahle/mpoly")
devtools::install_github("dkahle/bertini")
```





## Acknowledgements

This material is based upon work supported by the National Science Foundation under Grant Nos. [1622449](https://nsf.gov/awardsearch/showAward?AWD_ID=1622449) and [1622369](https://www.nsf.gov/awardsearch/showAward?AWD_ID=1622369).
